Graphs, partitioning and you

### 2016-01-31 evolutionaryComputation/2-practical/report.tex
spelling

\section{Methodology}
This time again I chose to use scala to solve this assignment. I was pleasently
surprised last time by the power of scala's combinators and hope this will be
the case again. I've become quite a fan of the langauge.

@@

So the file is stored in an imutable memory structure. This is possible
because the connections are just the number that essently work as pointers
if you have the graph at hand.

>>>>

\section{Methodology}
This time again I chose to use Scala to solve this assignment. I was pleasantly
surprised last time by the power of Scala's combinators and hope this will be
the case again. I've become quite a fan of the language.

@@

So the file is stored in an immutable memory structure. This is possible
because the connections are just the number that essentially work as pointers
if you have the graph at hand.
